Behavior Driven Development in Haskell

### 2012-05-27 paper.tex
Wording change
Add TBDs

HUnit does not provide any versatile mechanism to expect that an
exception is thrown.  So we propose a combinator for that.

@@

>>>>

HUnit does not provide any versatile mechanism to state that an action
should throw an exception.  So we propose a combinator for that.

@@

\begin{quote}
    TBD:
    \begin{itemize}
        \item
            This code snippet also illustrates how to deal with pure
            functions.
        \item
            {\tt seq} forces the exception.
        \item
            If {\tt x} is in {\tt NFData}, you may want to use {\tt
            deepseq} instead.
        \item
            The following would not work:
\begin{quote}\small\begin{verbatim}
(1 `div` 0) `shouldThrow` anyArithException
\end{verbatim}\end{quote}
        \item
            We think that pure functions that throw exceptions is bad
            API design.
    \end{itemize}
\end{quote}

TBD: Should we propose:
\begin{quote}\small\begin{verbatim}
shouldThrow_ :: (NFData a, Exception e) =>
  a -> (e -> Bool) -> Expectation
\end{verbatim}\end{quote}
